Measuring matter effects in Neutron star - Black hole binaries with Advanced LIGO

### 2015-05-19 Paper/paper.tex
added plots showing the width of 90% confidence interval for different recovered parameters

\textbf{Without BH-BH Templates}

@@

\textbf{Without NS-BH Templates}

@@

\caption{These figures show the unfaithfulness of the two EOB models we consider
in this paper against NR, with the top panel corresponding to SEOBNRv1 and the bottom panel to
SEOBNRv2. Note that the SEOBNRv1 model does not include component spins
higher than $+0.6$, we cannot compute its faithfulness in that region of binary parameter space.
We find that both models have high agreement with NR for smaller mass-ratios 
and/or small spin magnitudes. The SEOBNRv1 model significantly deviates from the NR 
waveform when the spin of the primay black hole reaches $\sim +0.6$ for $q=3$, while
SEOBNRv2 appears to be unfaithful to NR when \textit{both} black holes have high spin 
magnitudes, especially when both spins are aligned with the orbital angular momentum.

@@

\label{fig:SEOB_unfaith_TotalMass_Spin1z_Spin2z}

@@

\textbf{Without BH-BH Templates}
\textbf{Without NS-BH Templates}
\caption{These figures show the unfaithfulness of the two EOB models we consider
in this paper against NR, with the top panel corresponding to SEOBNRv1 and the bottom panel to
SEOBNRv2. Note that the SEOBNRv1 model does not include component spins
higher than $+0.6$, we cannot compute its faithfulness in that region of binary parameter space.
We find that both models have high agreement with NR for smaller mass-ratios 
and/or small spin magnitudes. The SEOBNRv1 model significantly deviates from the NR 
waveform when the spin of the primay black hole reaches $\sim +0.6$ for $q=3$, while
SEOBNRv2 appears to be unfaithful to NR when \textit{both} black holes have high spin 
magnitudes, especially when both spins are aligned with the orbital angular momentum.

@@

\label{fig:SEOB_unfaith_TotalMass_Spin1z_Spin2z}

@@

\textbf{Without BH-BH Templates}
\textbf{Without NS-BH Templates}
\caption{These figures show the unfaithfulness of the two EOB models we consider
in this paper against NR, with the top panel corresponding to SEOBNRv1 and the bottom panel to
SEOBNRv2. Note that the SEOBNRv1 model does not include component spins
higher than $+0.6$, we cannot compute its faithfulness in that region of binary parameter space.
We find that both models have high agreement with NR for smaller mass-ratios 
and/or small spin magnitudes. The SEOBNRv1 model significantly deviates from the NR 
waveform when the spin of the primay black hole reaches $\sim +0.6$ for $q=3$, while
SEOBNRv2 appears to be unfaithful to NR when \textit{both} black holes have high spin 
magnitudes, especially when both spins are aligned with the orbital angular momentum.
\label{fig:SEOB_unfaith_TotalMass_Spin1z_Spin2z}

@@

@@

\caption{These figures show the unfaithfulness of the two EOB models we consider
in this paper against NR, with the top panel corresponding to SEOBNRv1 and the bottom panel to
SEOBNRv2. Note that the SEOBNRv1 model does not include component spins
higher than $+0.6$, we cannot compute its faithfulness in that region of binary parameter space.
We find that both models have high agreement with NR for smaller mass-ratios 
and/or small spin magnitudes. The SEOBNRv1 model significantly deviates from the NR 
waveform when the spin of the primay black hole reaches $\sim +0.6$ for $q=3$, while
SEOBNRv2 appears to be unfaithful to NR when \textit{both} black holes have high spin 
magnitudes, especially when both spins are aligned with the orbital angular momentum.
\label{fig:SEOB_unfaith_TotalMass_Spin1z_Spin2z}

>>>>

\textbf{With BH-BH Templates}

@@

\textbf{With NS-BH Templates}

@@

\caption{These figures show the (fractional) difference between the median value of
recovered posterior distribution for binary chirp mass and the actual injected chirp mass,
as a function of the signal-to-noise-ratio (SNR) of the injected signal.
The top and bottom panels show results for parameter estimation performed using
waveform templates without and with NS matter effects included, respectively.
In each row, the left and right panel correspond to 
$q=m_\mathrm{BH}/m_\mathrm{NS}=\{2,3\}$, respectively. 
In each panel, the color of the curves correspond to the value of NS deformability 
parameter, and line style correspond to the dimensionless spin on the BH 
($\chi_\mathrm{BH}\equiv \dfrac{a}{m_\mathrm{BH}^2}$).

@@

\label{fig:TNT_chirpMassBias_vs_SNR_q23}

@@

	\textbf{With BH-BH Templates}
	\includegraphics[width=2\columnwidth]{plots/TN_chirpMassCIWidth90_vs_SNR_q23.pdf}\\ 
	\textbf{With NS-BH Templates}
	\includegraphics[width=2\columnwidth]{plots/TT_chirpMassCIWidth90_vs_SNR_q23.pdf}%\quad
	\caption{These figures show the narrowing of the $90\%$ confidence 
		interval (recovered) for chirp mass, as a function of the 
		signal-to-noise-ratio (SNR). Note that the confidence interval
                width is normalized by the true parameter value.
                The binary parameters, i.e. black hole spin,
                mass-ratio, NS tidal deformability, are all depicted in the 
                same way as in Fig.~\ref{fig:TNT_chirpMassBias_vs_SNR_q23}.

@@

	\label{fig:TNT_chirpMassCIWidth90_vs_SNR_q23}

@@

\textbf{With BH-BH Templates}
\textbf{With NS-BH Templates}
\caption{This figure is similar to Fig.~\ref{fig:TNT_chirpMassBias_vs_SNR_q23},
with the difference that we consider the systematic bias in the dimensionless
mass-ratio $\eta$ here.}
\label{fig:TNT_EtaBias_vs_SNR_q23}

@@

	\textbf{With BH-BH Templates}
	\includegraphics[width=2\columnwidth]{plots/TN_EtaCIWidth90_vs_SNR_q23.pdf}\\ 
	\textbf{With NS-BH Templates}
	\includegraphics[width=2\columnwidth]{plots/TT_EtaCIWidth90_vs_SNR_q23.pdf}%\quad
	\caption{This figure is similar to Fig.~\ref{fig:TNT_chirpMassCIWidth90_vs_SNR_q23},
		with the difference that we consider the confidence intervals in the recovery
		of the dimensionless
		mass-ratio $\eta$ here.}
	\label{fig:TNT_EtaCIWidth90_vs_SNR_q23}
\textbf{With BH-BH Templates}
\textbf{With NS-BH Templates}
\caption{This figure is similar to Fig.~\ref{fig:TNT_chirpMassBias_vs_SNR_q23},
with the differences that we consider the systematic bias in the dimensionless
spin on the BH here, and that the differences shown are absolute and not
fractions of the injected spin.}
\label{fig:TNT_BHspinBias_vs_SNR_q23}
	\textbf{With BH-BH Templates}
	\includegraphics[width=2\columnwidth]{plots/TN_BHspinCIWidth90_vs_SNR_q23.pdf}\\ 
	\textbf{With NS-BH Templates}
	\includegraphics[width=2\columnwidth]{plots/TT_BHspinCIWidth90_vs_SNR_q23.pdf}%\quad
	\caption{This figure is similar to Fig.~\ref{fig:TNT_chirpMassCIWidth90_vs_SNR_q23},
		with the difference that we consider the confidence intervals in the recovery
		of the dimensionless spin on the BH $\chi_\mathrm{BH}$ here.}
	\label{fig:TNT_BHspinCIWidth90_vs_SNR_q23}
\begin{figure*}
\textbf{With NS-BH Templates}

@@

\caption{This figure is similar to the bottom row of
Fig.~\ref{fig:TNT_chirpMassBias_vs_SNR_q23}, with the difference that  we
consider the NS tidal parameter $\Lambda$ here.}
\label{fig:TT_NSLambdaBias_vs_SNR_q23}
\begin{figure*}
	\textbf{With NS-BH Templates}
	\includegraphics[width=2\columnwidth]{plots/TT_NSLambdaCIWidth90_vs_SNR_q23.pdf}
	\caption{This figure is similar to the bottom row of
		Fig.~\ref{fig:TNT_chirpMassCIWidth90_vs_SNR_q23}, with the difference that  we
		consider the NS tidal parameter $\Lambda$ here.}
	\label{fig:TT_NSLambdaCIWidth90_vs_SNR_q23}
